---
title: "Media Monitor II"
author: "MD Shuey"
date: "February 9, 2019"
output: html_document
---
# Introduction

The media relations of any person or entity are vital signs of influence. For a country, this has been referred to as "soft power", usually in the context of cultural transmission. How and when national or international media sources choose to report on a country's affairs are questions of importance for national external relations. 

The [NewsAPI]("newsapi.org") is an online HTML-based interface that allows the user to view article and blogpost information from hundreds of websites in real time. This will be the tool that I intend to use to monitor the test subject of a given entity (here, the country of Brazil) from a starting period to an ending period.

```{r setup, include=FALSE, echo=FALSE}
devtools::install_github("MDshuey/newsAPI")
library(newsAPI)
library(tidyverse)
library(httr)
"c180fe7feb8e412583a6bd1acbcecab7" -> NEWSAPI_KEY
cat(
  paste0("NEWSAPI_KEY=", NEWSAPI_KEY),
  append = TRUE,
  fill = TRUE,
  file = file.path("~", ".Renviron")
)
```
``` {r}
#Examining sources
src.en=get_sources(language="en")
src.en$category <- as.factor(src.en$category)
src.all=get_sources()

#Retrieving article data
df <- get_articles(keyword="brazil", sources="cnn", word="brazil")
recent <- do.call("rbind", recent)

#run get_articles 31 times, once for each day since 31 days ago, and convert it all to one dataframe
daily_recaps <- function(from = Sys.Date()-30, ...) {
  x <- seq.Date(from = as.Date(from), to = Sys.Date(), by="day")%>%as.character()
  out <- vector("list", length(x))
  for (i in seq_along(x)) {
    out[[i]] <- get_articles(..., from=x[[i]], to=x[[i]])
  }
  out <- do.call("rbind", out)
  for (i in 2:length(out)) {
    out[,i] <- unlist(out[,i])
  }
  out
}
test10 <- daily_recaps(from="2019-09-10", keyword="China")

#parameter testing
br.data.rel <- daily_recaps(keyword="+brazil", from = "2019-09-21", sortBy="relevancy")
br.data.pop <- daily_recaps(keyword="brazil", from = "2019-09-21", sortBy="popularity")

```
You may exclude entertainment and sports, however in social contexts they are indicators of soft power for a country, or may be relevant for organizations checking their presence in online media.
``` {r tm}
library(tm)
library(SnowballC)

# Function for text mining content
cleandocs <- function(corp){
corp <- tm_map(corp, removePunctuation)
corp <- tm_map(corp, content_transformer(tolower))
corp <- tm_map(corp, removeWords, stopwords("english"))
corp <- tm_map(corp, stemDocument)
corp
}

#Performing an example
corp <- Corpus(VectorSource(br.data.rel$title))
corp <- cleandocs(corp)
matrix=DocumentTermMatrix(corp)

wordfreq = findMostFreqTerms(matrix, 100)
wordfreq=wordfreq$`1`
wordfreq=as.data.frame(wordfreq)
wordfreq=setDT(wordfreq, keep.rownames=T)
head(wordfreq, 25)

```

## Acknowledgements 

Thanks to NewsAPI.org for making such an accessible API.
Thanks to GitHub user mKearney for originally writing the newsAPI wrapper for R.