---
title: "Media Monitor II"
author: "MD Shuey"
date: "February 9, 2019"
output: html_document
---
# Introduction

The media relations of any person or entity are vital signs of influence. For a country, this has been referred to as "soft power", usually in the context of cultural transmission. How and when national or international media sources choose to report on a country's affairs are questions of importance for national external relations. 

The [NewsAPI]("newsapi.org") is an online HTML-based interface that allows the user to view article and blogpost information from hundreds of websites in real time. This will be the tool that I intend to use to monitor the test subject of a given entity (here, the country of Brazil) from a starting period to an ending period.

```{r setup, include=FALSE, echo=FALSE}
devtools::install_github("MDshuey/newsAPI")
library(newsAPI)
library(tidyverse)
library(httr)
"c180fe7feb8e412583a6bd1acbcecab7" -> NEWSAPI_KEY
cat(
  paste0("NEWSAPI_KEY=", NEWSAPI_KEY),
  append = TRUE,
  fill = TRUE,
  file = file.path("~", ".Renviron")
)
```
``` {r}

src.en=get_sources(language="en")
src.en$category <- as.factor(src.en$category)
src.all=get_sources()

src.pt=get_sources(language="pt")

df <- get_articles(keyword="brazil", sources="cnn")
nonsoft.list <- which(src.en$category %in% c("entertainment", "sports"))
recent <- lapply(src.en$id[-nonsoft.list], get_articles, keyword="brazil")
recent <- do.call("rbind", recent)
Jan12=get_articles(keyword="brazil", from="2019-01-12", to="2019-01-12")
#run get_articles 31 times, once for each day since 31 days ago, and convert it all to one dataframe
br.data <- lapply(
  seq.Date(from=Sys.Date()-30, to=Sys.Date(), by="day"),
  get_articles, keyword="brazil",
                  pageSize=100)
br.data <- do.call("rbind", br.data)
br.data <- rbind(br.data, Jan12)
```
You may exclude entertainment and sports , however in social contexts they are indicators of soft power for a country, or may be relevant for organizations checking their presence in online media.

## Acknowledgements 

Thanks to NewsAPI.org for making such an accessible API.
Thanks to GitHub user mKearney for originally writing the newsAPI wrapper for R.